Linked Open Social Data for Scientific Benchmarking (Supporting Information document)

### 2016-07-28 misc/overallText.tex
enhanced page sizes

Database consists of 37467423 triples, 3088219 edges yield by interactions or relations, 382735 participants and 229008584 characters. Among all snapshots, 63 are ego snapshots, 53 are group snapshots; 45 have interaction edges, 89 have friendship edges; 42 have text content from messages.

>>>>

The LOSD database consists of 34,120,026 triples, 3,172,927 edges yield by interactions or relations, 382,568 participants and 253,155,020 characters. Among all snapshots, 63 are ego snapshots, 54 are group snapshots; 49 have interaction edges, 89 have friendship edges; 43 have text content from messages.

### 2016-07-28 supportingInformation.tex
enhanced page sizes

\end{frontmatter}
% \pdfpageheight 8in
\tableofcontents
\clearpage
\section{General guidance}
% \paperheight = 200pt
In this document we provide diagrams
for the provenances in the LOSD:
Facebook, Twitter, IRC, Email, ParticipaBR, Cidade Democrática and AA.
Each provenance diagram was broken in two, one presents the relations
among main classes (blue nodes) and data types (orange nodes), the other presents metadata on the
snapshot.
Every class instance is related to the snapshot instance
by the triple \textttt{class\_uri po:snapshot snapshot\_uri}.
Such triples are omitted for simplicity.
Due to the large number of relations, the rendering of diagrams are
automatized and displays some overlaps.
Even so, the images are useful for grasping what is in current LOSD
and for conducting explorations.
Edges in the diagrams have:
\begin{itemize}
    \item green color if representing an OWL existential
class restriction (all individuals from the class present at least one triple with
the property as predicate);
    \item inverted nip if representing an OWL universal class
        restriction (all individuals presenting triples with the
        property as predicate are from the class);
    \item full edges (non-dashed) if representing a functional property
        axiom (there is at most one triple with the property as the
        predicate for each individual).
\end{itemize}

@@

\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Facebook};}
    paper=graphics
][scale=.5]{ontologies/facebook-legacy-Auricultura10042013Meta.ttl/draw.png}

@@

\pdfpageheight 4in
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge
  Twitter };}
    paper=graphics
][scale=.5]{ontologies/twitter-legacy-arenaNETmundialTweet00000.ttl/draw.png}

@@

\section{Email data}
Each IRC snapshot is yield by an Email list.
Interactions is yield through \textttt{po:replyTo} relations
although \textttt{po:to} and \textttt{po:cc} can also be considered.
the email body is given by \textttt{po:text} relations while
\textttt{po:cleanText} has the text with lines removed where they are
trivially from previous messages or computer code.
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.4]{ontologies/gmane-legacy-.linux.audio.devel1-20000Email00000.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.5]{ontologies/gmane-legacy-linux.audio.devel1-20000Meta.ttl/draw.png}

@@

\section{Cidade Democrática data}
The Cidade Democrática snapshot is yield by a data dump donated by the system
administrators of the civil society social participation portal Cidade
Democrática.
This snapshot holds a complex structure of both
Topics/Inspirations/Observatories/Supports/Competitions/Prizes
and of State/City/Neighborhood/Place.
The language used is mainly Brazilian Portuguese.
Due to the higher complexity of the diagram, an additional figure is
given rendered with another layout algorithm
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Cidade
  Democrática};}
    paper=graphics
][scale=.4]{ontologies/cidadedemocratica00000.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Cidade
  Democrática};}
    paper=graphics
][scale=.4]{ontologies/cidadedemocratica00000.ttl/draw_circo.png}

@@

\section{AA data}
The AA (Algorithmic Autoregulation) snapshots are yield by a data dump donated by the system
administrators and by a mined IRC log.
The system pursue simplicity and most of data consists of detached
shouts with \textttt{po:text} and \textttt{po:author}.
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge AA};}
    paper=graphics
][scale=.6]{ontologies/aairc.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge AA};}
    paper=graphics
][scale=.7]{ontologies/aaircMeta.ttl/draw.png}

>>>>

\end{frontmatter}
\newcommand{\foo}{\textheight}
\newcommand{\foobar}{\pdfpageheight}
% \pdfpageheight 8in
\tableofcontents
\clearpage
\section{General guidance}
% \paperheight = 200pt
In this document we provide diagrams
for the provenances in the LOSD:
Facebook, Twitter, IRC, Email, ParticipaBR, Cidade Democrática and AA.
Each provenance diagram was broken in two, one presents the relations
among main classes (blue nodes) and data types (orange nodes), the other presents metadata on the
snapshot.
Every class instance is related to the snapshot instance
by the triple \textttt{class\_uri po:snapshot snapshot\_uri}.
Such triples are omitted for simplicity.
Due to the large number of relations, the rendering of diagrams are
automatized and displays some overlaps.
Even so, the images are useful for grasping what is in current LOSD
and for conducting explorations.
Edges in the diagrams have:
\begin{itemize}
    \item green color if representing an OWL existential
class restriction (all individuals from the class present at least one triple with
the property as predicate);
    \item inverted nip if representing an OWL universal class
        restriction (all individuals presenting triples with the
        property as predicate are from the class);
    \item full edges (non-dashed) if representing a functional property
        axiom (there is at most one triple with the property as the
        predicate for each individual).
\end{itemize}

@@

\textheight = 2in
\pdfpageheight 5in
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Facebook};}
    paper=graphics
][scale=.5]{ontologies/facebook-legacy-Auricultura10042013Meta.ttl/draw.png}

@@

\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge
  Twitter };}
    paper=graphics
][scale=.5]{ontologies/twitter-legacy-arenaNETmundialTweet00000.ttl/draw.png}

@@

\section{Email data}
Each IRC snapshot is yield by an Email list.
Interactions is yield through \textttt{po:replyTo} relations
although \textttt{po:to} and \textttt{po:cc} can also be considered.
the email body is given by \textttt{po:text} relations while
\textttt{po:cleanText} has the text with lines removed where they are
trivially from previous messages or computer code.
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.4]{ontologies/gmane-legacy-linux.audio.devel1-20000Email00000.ttl/draw.png}
\textheight = 3in
\pdfpageheight 6in
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.5]{ontologies/gmane-legacy-linux.audio.devel1-20000Meta.ttl/draw.png}

@@

\section{Cidade Democrática data}
The Cidade Democrática snapshot is yield by a data dump donated by the system
administrators of the civil society social participation portal Cidade
Democrática.
This snapshot holds a complex structure of both
Topics/Inspirations/
Observatories/Supports/Competitions/Prizes
and of State/City/Neighborhood/Place.
The language used is mainly Brazilian Portuguese.
Due to the higher complexity of the diagram, an additional figure is
given rendered with another layout algorithm
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Cidade
  Democrática};}
    paper=graphics
][scale=.4]{ontologies/cidadedemocratica00000.ttl/draw.png}
\textheight = 2in
\pdfpageheight 5in
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Cidade
  Democrática};}
    paper=graphics
][scale=.4]{ontologies/cidadedemocratica00000.ttl/draw_circo.png}

@@

\section{AA data}
The AA (Algorithmic Autoregulation) snapshots are yield by a data dump donated by the system
administrators and by a mined IRC log.
The system pursue simplicity and most of data consists of detached
shouts with \textttt{po:text} and \textttt{po:author}.
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge AA};}
    paper=graphics
][scale=.6]{ontologies/aairc.ttl/draw.png}
\textheight = 7in
\pdfpageheight \foobar
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge AA};}
    paper=graphics
][scale=.7]{ontologies/aaircMeta.ttl/draw.png}

### 2016-07-28 tables/nsnapshots.tex
enhanced page sizes

\begin{table*}[h!]
\begin{center}
\caption{Number of snapshots from each provenance. Every snapshot is a \texttt{po:Snapshot}; there are three types of the \texttt{po:AASnapshot} class.}
\begin{tabular}{| l | c |}\hline
\textbf{snapshot provenance} & \textbf{number of snapshots} \\\hline\hline
http://purl.org/socialparticipation/po/AAIRCSnapshot & 5 \\\hline
http://purl.org/socialparticipation/po/AAMongoSnapshot & 1 \\\hline
http://purl.org/socialparticipation/po/AAMysqlSnapshot & 1 \\\hline
http://purl.org/socialparticipation/po/AASnapshot & 7 \\\hline
http://purl.org/socialparticipation/po/CidadeDemocraticaSnapshot & 1 \\\hline
http://purl.org/socialparticipation/po/FacebookSnapshot & 88 \\\hline
http://purl.org/socialparticipation/po/IRCSnapshot & 4 \\\hline
http://purl.org/socialparticipation/po/ParticipabrSnapshot & 1 \\\hline
http://purl.org/socialparticipation/po/TwitterSnapshot & 16 \\\hline\hline
http://purl.org/socialparticipation/po/Snapshot & 116 \\\hline
\end{tabular}\end{center}
\end{table*}

>>>>

\begin{table*}[h!]
\begin{center}
\caption{Number of snapshots from each provenance. Every snapshot is a \texttt{po:Snapshot}; there are three types of the \texttt{po:AASnapshot} class.}
\begin{tabular}{| l | c |}\hline
\textbf{snapshot provenance} & \textbf{number of snapshots} \\\hline\hline\hline
http://purl.org/socialparticipation/po/Snapshot & 117 \\\hline
\end{tabular}\end{center}
\end{table*}
